\textbf{Learning semi-Markovian DAGs with flow-based VAE}

### 2023-12-05 Tex/paper.tex
commit

We compare first the performance of our method with DAG-GNN in the case where the noise variables are independent. To be specific, we consider the case where the noise variables follow an independent Gaussian, Laplace, and exponential distribution. The results of the experiments are shown in Figure \ref*{SHD_FDR_gaussian}, \ref*{SHD_FDR_laplace}, and \ref*{SHD_FDR_exponential}. In all cases, our method outperforms DAG-GNN in terms of both SHD and FDR.\\

@@

>>>>

We compare first the performance of our method with DAG-GNN in the case where the noise variables are independent. To be specific, we consider the case where the noise variables follow an independent Gaussian, Laplace, and exponential distribution. The results of the experiments are shown in Figure \ref*{SHD_FDR_laplace}, and \ref*{SHD_FDR_exponential}. In all cases, our method outperforms DAG-GNN in terms of both SHD and FDR.\\

@@

\begin{figure}[H]
    \centering
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{fig/SHD_independence_exponential.pdf}
        \caption{SHD with exponential noise}
        \label{SHD_exponential}
    \end{subfigure}
    \hfill
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{fig/FDR_independence_exponential.pdf}
        \caption{FDR with exponential noise}
        \label{FDR_exponential}
    \end{subfigure}
    \caption{SHD and FDR with exponential noise}
    \label{SHD_FDR_exponential}
\end{figure}
